\morus: Biases in the Stream

### 2018-05-09 morusAC_01_Introduction.tex
tense consistency

\subsubsection*{Related Work.}
In the submission document, the designers discuss the security of \morus against
several attacks, including algebraic, differential, and guess-and-determine attacks,
as well as the general design rationale of the initialization, encryption process, and finalization \cite{MORUS}.
The main focus is on differential properties, whereas not many details are given for the other attack vectors.
In third-party analysis,
Mileva et~al.~\cite{balkancryptsecMilevaDV15} propose a distinguisher for the nonce-reuse setting and practically evaluate the differential behaviour of toy variants of \morus.
Dwivedi et~al.~\cite{cryptoeprint:2016:1053} discussed the applicability of SAT solvers for state recovery, but the resulting complexity of $2^{370}$ for \morus[640] is well beyond the security claim.
Dwivedi et~al.~\cite{secryptDwivediMW17} later proposed key-recovery attacks for \morus[1280] if the initialization is reduced to 3.6 out of 16 rounds and discussed the security of \morus against internal differentials and rotational cryptanalysis.
Salam et~al.~\cite{trustcomSalamSBDPW17} applied cube attacks to obtain distinguishers for up to 5 out of 16 rounds of the initialization of \morus[1280] with negligible complexity.
Additionally, 
Kales et~al.~\cite{cryptoeprint:2017:1137} and
Vaudenay and Viz\'{a}r \cite{cryptoeprint:2017:1147}
independently proposed state-recovery and forgery attacks on \morus in a nonce-misuse setting with negligible data and time complexities.

>>>>

\subsubsection*{Related Work.}
In the submission document, the designers discuss the security of \morus against
several attacks, including algebraic, differential, and guess-and-determine attacks,
as well as the general design rationale of the initialization, encryption process, and finalization \cite{MORUS}.
The main focus is on differential properties, whereas not many details are given for the other attack vectors.
In third-party analysis,
Mileva et~al.~\cite{balkancryptsecMilevaDV15} propose a distinguisher for the nonce-reuse setting and practically evaluate the differential behaviour of toy variants of \morus.
Dwivedi et~al.~\cite{cryptoeprint:2016:1053} discuss the applicability of SAT solvers for state recovery, but the resulting complexity of $2^{370}$ for \morus[640] is well beyond the security claim.
Dwivedi et~al.~\cite{secryptDwivediMW17} also propose key-recovery attacks for \morus[1280] if the initialization is reduced to 3.6 out of 16 rounds and discuss the security of \morus against internal differentials and rotational cryptanalysis.
Salam et~al.~\cite{trustcomSalamSBDPW17} apply cube attacks to obtain distinguishers for up to 5 out of 16 rounds of the initialization of \morus[1280] with negligible complexity.
Additionally, 
Kales et~al.~\cite{cryptoeprint:2017:1137} and
Vaudenay and Viz\'{a}r \cite{cryptoeprint:2017:1147}
independently propose state-recovery and forgery attacks on \morus in a nonce-misuse setting with negligible data and time complexities.
